Pathogen Spillover - dissertation chapter

### 2016-07-29 pathogen-spillover-diss-ch.Rmd
Add figure of oak infection.

rstemps_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), hrs1422_wet)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Number of hours") +
      ggtitle("Wet-ours 14-22 C")

```

>>>>

rstemps_figure <- temps_figure + 
      geom_boxplot(aes(as.factor(sample_year), hrs1422_wet)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Number of hours") +
      ggtitle("Wet-hours 14-22 C")

oak_infection_figure <- temps_figure +
      geom_bar(aes(as.factor(sample_year), inf_oak_ct), stat = "identity") +
      # geom_boxplot(aes(as.factor(sample_year), inf_oak_ct)) +
      theme_bw() +
      xlab("Sample Year") +
      ylab("Number of infected oaks") +
      ggtitle("Incident oak infection")
```
